\documentclass[a4paper]{deedy-resume}

\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{fontawesome}
\newfontfamily{\FA}{Font Awesome 5 Free-Solid}
\newfontfamily{\FAR}{Font Awesome 5 Free-Regular}
\newfontfamily{\FAB}{Font Awesome 5 Brands-Regular}
\usepackage{constants}
\definecolor{dark-red}{rgb}{0.75,0.15,0.15}
\definecolor{dark-green}{rgb}{0.15,0.4,0.15}
\definecolor{medium-blue}{rgb}{0,0,0.5}
\usepackage{hyperref}
\hypersetup{plainpages=false,pdfpagelabels,unicode,draft=false,colorlinks=true,linkcolor={dark-red},citecolor={dark-green},urlcolor={dark-red}}

% FontAwesome Icons
\def\phone{{\FA \faPhone}}
\def\envelope{{\FA \faEnvelopeAlt}}
\def\star{{\FA \faStar}}
\def\starEmpty{{\FAR \faStar}}
\def\starHalf{{\FA \faStarHalf}}
\def\github{{\FAB \faGithub}}
\def\linkedIn{{\FAB \faLinkedin}}

\begin{document}
%----------------------------------------------------------------------------------------
% TITLE SECTION
%----------------------------------------------------------------------------------------
\namesection{Ivo}{Hrádek}{
    \runsubsection{Software Engineer}
}
%----------------------------------------------------------------------------------------
% LEFT COLUMN
%----------------------------------------------------------------------------------------
\begin{minipage}[t]{0.32\textwidth} % The left column takes up 33% of the text width of the page
%------------------------------------------------
% Contact
%------------------------------------------------
\section{Contact} % Your contact information
\phone\hspace{8pt}\telnumber \\
\envelope\hspace{8pt}\href{mailto:ivohradek@gmail.com}{ivohradek@gmail.com}
%------------------------------------------------
% Links
%------------------------------------------------
\section{Links}
\github\hspace{8pt}\href{https://github.com/hradecek}{\bf hradecek} \\
\linkedIn\hspace{9pt}\href{https://www.linkedin.com/in/ivo-hr\%C3\%A1dek-01baa8115/}{\bf ivohradek}
%------------------------------------------------
% Education
%------------------------------------------------
\section{Education}
\runsubsection{Masaryk University}\\
\descript{Bachelor in Computer Science}
\location{Graduated June 2015 | Brno, CZ}
Conc. in Computer Systems and Data Processing\\
\sectionspace
%------------------------------------------------
\runsubsection{Secondary Technical School of Mechanical and Electrical Engineering}\\
\location{Graduated June 2012 | Nitra, SK}
Conc. in Industrial Informatics\\
\sectionspace
%------------------------------------------------
% Coursework
%------------------------------------------------
\section{Coursework}
\subsection{Graduate}
\textbullet{} UNIX – Programming and System\\\hspace{5.7pt} Management I and II\\
\textbullet{} MS Windows Systems Management I\\
\textbullet{} Seminar on Functional Programming\\
\textbullet{} Advanced Functional Programming\\
\textbullet{} Seminar in Java programming\\
\sectionspace
%------------------------------------------------
% Skills
%------------------------------------------------
\section{Skills}
\subsection{Programming}
\star\star\star\star\star\star\\
Java\\
\star\star\star\star\starEmpty\\
PHP\\
\location{\star\star\star\starEmpty\starEmpty}
Haskell \textbullet{} Python \textbullet{} C\\
\location{\star\starEmpty\starEmpty\starEmpty\starEmpty}
C++ \textbullet{} C\# \textbullet{} Groovy \textbullet{} Perl\\
\sectionspace
\subsection{Development Tools}
GIT \textbullet{} SVN \textbullet{} Maven \textbullet{} Gradle
\sectionspace
\subsection{Database Platforms}
MySQL
\end{minipage}
\hfill
%----------------------------------------------------------------------------------------
% RIGHT COLUMN
%----------------------------------------------------------------------------------------
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page
%------------------------------------------------
% Experience
%------------------------------------------------
\section{Experience}
\runsubsection{Tieto}
\descript{| Software Developer\hfill\small June 2018 - Present}
\location{Software Defined Infrastracture}
\vspace{\topsep}
Software Defined Infrastructure provides the capability to control and configure hardware from a central management platform into virtual performance-optimized datacenters, which provides flexibility for NVF solutions.
 
\vspace{\topsep}
\textbf{Responsibilities:}
\vspace{\topsep}
\begin{tightitemize}
    \item develop new features,
    \item improving legacy code,
    \item resolving customer issues,
    \item participate in new functionality research.
\end{tightitemize}
\sectionspace
\runsubsection{Red Hat}
\descript{| Quality Engineer\hfill\small May 2016 - December 2017}
\location{JBoss EAP}
\vspace{\topsep}
JBoss EAP Quality Engineering team was integral part in serving of tested, tuned and reliable product to Red Hat's customers.

\vspace{\topsep}
\textbf{Responsibilities:}
\vspace{\topsep}
\begin{tightitemize}
    \item defining testing strategies,
    \item develop test automation frameworks,
    \item document new bugs,
    \item participate in product releases.
\end{tightitemize}
\sectionspace
%------------------------------------------------
\runsubsection{Foxytouch}
\descript{| Software Developer\hfill\small December 2015 - May 2016}
\location{FoxyAdmin}
\vspace{\topsep}
FoxyAdmin was modular and lightweight content management system (CMS) written in Laravel5 (PHP), that was developed due to rising demand of small sized companies for customizable system.

\vspace{\topsep}
\textbf{Responsibilities:}
\begin{tightitemize}
    \item software architecture design (UML),
    \item database design (SQL),
    \item developed new features and modules based on customer's requirements,
    \item provided bug fixes.
\end{tightitemize}
\sectionspace
%------------------------------------------------
\runsubsection{University}
\descript{| Bachelor Thesis\hfill\small May 2015}
\location{APK2XML}
\vspace{\topsep}
The bachelor thesis analysed structure of the Android package~(APK), Dalvik executable~(DEX) file formats and fully described undocumented XML binary format.
Result of theoretical research was implementation performing conversion from binary XML to text XML.

\vspace{\topsep}
\textbf{Learned:}
\begin{tightitemize}
    \item reverse engineering,
    \item Java programming,
    \item Android architecture.
\end{tightitemize}
\sectionspace
\end{minipage}
%------------------------------------------------
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page
\runsubsection{High School}
\descript{| Student Project\hfill\small January 2012}
\location{Mini-PLC}
\vspace{\topsep}
Student project focused on creation of a low cost \textit{programable logic controller}~(PLC).
Determined by an underlaying microcontroller, Mini-PLC implemented variety of basics and complex functions programmable through a simple graphical user interface (GUI) in form of ladder logic.
Mini-PLC was featured with ethernet module providing the possibility of state monitoring.

\vspace{\topsep}
\textbf{Learned:}
\vspace{\topsep}
\begin{tightitemize}
    \item algorithm design,
    \item microcontroller programming in C,
    \item C\# and WPF basics.
\end{tightitemize}
\vspace{\topsep}
\textbf{Awards:}
\begin{tightitemize}
    \item 1\textsuperscript{st} place in Technical Idea of the year,
    \item presented at Student Research and Professional Activities nationwide meeting.
\end{tightitemize}
%\sectionspace
\end{minipage}
\end{document}
